My title

### 2024-03-10 paper/paper.qmd
putting together the model so far

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Talia Fabregas
  - Fatimah Yunusa
  - A
thanks: "Code and data are available at: https://github.com/taliafabs/US-Election-Forecast.git"
date: today
date-format: long
abstract: "Forecasting the 2024 US Presidential Election."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
# library(rstanarm)
library(readr)
library(ggplot2)
```

@@

@@

The remainder of this paper is structured as follows. @sec-data

@@

@@

@@

@@

The goal of our modelling strategy is twofold. Firstly,...

@@

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Talia Fabregas
  - Fatimah Yunusa
  - Aamishi Sundeep
thanks: "Code and data are available at: https://github.com/taliafabs/US-Election-Forecast-2024.git"
date: today
date-format: long
abstract: "The 2024 U.S. Presidential Election ..."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(janitor)
library(rstanarm)
library(readr)
library(ggplot2)
```

@@

The 2024 U.S. Presidential Election will take place on Tuesday November 5 2024. Incumbent President Joseph R. Biden Jr. will seek a second term. Former President Donald J. Trump GOP nominee.

Delegates to secure the nomination, Nikki Haley has dropped out of GOP

@@

The remainder of this paper is structured as follows. @sec-data discusses the survey and post-stratification data used.

@@

-   2024 US Presidential Election

-   how consequential this election is

-   what is on the ballot

-   women's rights

-   trump's project 2025 thing

@@

@citeR was usd

@@

### Survey Data figures and tables go here

@@

logistic regression

binary

predicts support for trump or biden

@@

# first_model <-
#   readRDS(file = here::here("models/first_model.rds"))
```

@@

# modelsummary::modelsummary(
#   list(
#     "First model" = first_model
#   ),
#   statistic = "mad",
#   fmt = 2
# )
```

@@

# pp_check(first_model) +
#   theme_classic() +
#   theme(legend.position = "bottom")
# 
# posterior_vs_prior(first_model) +
#   theme_minimal() +
#   scale_color_brewer(palette = "Set1") +
#   theme(legend.position = "bottom") +
#   coord_flip()
```

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2
# 
# plot(first_model, "trace")
# 
# plot(first_model, "rhat")
```
